\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-01 doc/publications/plos16/plos16.tex
Updated equasions in methods section

The model paramters are $w_i = 1/\sqrt{2^{i-1}}$ for $i =1,\ldots 5$ and we set 
$$
z =  \sum_{i=1}^{i=5} {w_i x_i}.
$$
We let $\sigma_\epsilon^2 = Var(z)(1- 0.125)/0.125 $ and then 
$y =   z + \epsilon$ where $\epsilon \sim  N(0, \sigma_\epsilon^2).$
The dichotomous response is generated by thresholding $y$ at the $0.8$ quantile.

>>>>

The model paramters are $w_i = 1/\sqrt{2^{i-1}}$ for $i =1,\ldots 5$ and we set 
$$
z =  \sum_{i=1}^{i=5} {w_i x_i}.
$$
We let $\sigma_\epsilon^2 = Var(z)(1-\theta)/\theta $  where $\theta$ is a parameter controling the fraction of variance explained by the infomative variables and in our study we chose $\theta = 0.125$ . Then 
$y =   z + \epsilon$ where $\epsilon \sim  N(0, \sigma_\epsilon^2).$
The dichotomous response is generated by thresholding $y$ at the $0.5$ quantile.

$$
\ddot{y} =    \left\{ \begin{array}{rcl}
			  0 & \mbox{for} & y \leq Q2(y) \\
			  1 & \mbox{for} & y > Q2(y)
		 \end{array}\right.
$$
